### 2021-10-12 docs/paper/sections/1_introduction.tex

In essence, our proposed approach consists of three steps:
\begin{enumerate*}[label=(\roman*)]
	\item collect downstream dependency repositories from public clouds,
	\item mine package usage samples from these dependencies by using a type analyzer,
	and \item aggregate and present these usage data to the user.
\end{enumerate*}

>>>>

In essence, our proposed approach consists of three steps:
\begin{enumerate*}[label=(\roman*)]
	\item collect downstream dependency repositories from public clouds,
	\item mine package usage samples from these dependencies by using a type analyzer,
	and \item aggregate and present these usage data to the package developer.
\end{enumerate*}

### 2021-10-12 docs/paper/sections/2_related_work.tex

However, the precision of ASTs is limited for \emph{dynamically typed} languages such as JavaScript or Python.
As opposed to static typing, the value type of an expression in a dynamically typed language may be unknown at the compile time of the program.
For this reason, a \emph{type analysis} can be performed to predict the runtime types of all expressions in the AST \citep{jensen2009type}.
Usually, this is accomplished by analyzing the control flow of a program and inferring the possible types of every variable or function.
Another useful data structure for enhancing type information are \emph{call graphs} that are either gained \emph{statically} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamically} (i.e., empirically recorded during program execution).
While the latter method has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.
Many solutions exist that analyze the structure of programs and extract relevant information to build call graphs:

>>>>

However, the precision of ASTs is limited for \emph{dynamically typed} languages such as JavaScript or Python.
As opposed to static typing, the value type of an expression in a dynamically typed language may be unknown at the compile time of the program.
For this reason, a \emph{type analysis} can be performed to predict the runtime types of all expressions in the AST \citep{jensen2009type}.
Usually, this is accomplished by analyzing the control flow of a program and inferring the possible types of every variable or function.
Another useful data structure for enhancing type information is \emph{call graphs} that are either gained \emph{statically} (i.e., the result of a theoretical analysis of the source code) or \emph{dynamically} (i.e., empirically recorded during program execution).
While the latter method has a higher potential for including a maximum of contextual information, the former has the advantage of being applicable to a larger probe of source code for that no concrete entry points are available.
Many solutions exist that analyze the structure of programs and extract relevant information to build call graphs:

### 2021-10-12 docs/paper/sections/3_approach.tex

To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate \emph{abstract syntax forest}F (ASF, i.e., a set of ASTs).

>>>>

To do so, we start by parsing the source code of every dependency repository as well as the source code of the target package each into a separate \emph{abstract syntax forest} (ASF, i.e., a set of ASTs).

### 2021-10-12 docs/paper/sections/5_evaluation.tex

Besides the precision of collected dependencies, their recall is also of interest.
As the dependencies are collected in excerpts from two very large datasets, a quantitative analysis of false-negative hits based on manual annotation of these datasets would be too expensive for this paper.
Nevertheless, there are some causes that will prevent a dependency from being found by our methods:

@@

	\centering
	\begin{threeparttable}
		% Fix font size of \thead
		\renewcommand\theadfont{\normalsize}
		\input{sections/5_evaluation/resqu1/performance}
		\begin{tablenotes}
			\footnotesize
			\item[\alphtnotetext{1}] Hardware specifications of the test machine: 7 vCPUs Intel Xeon Cascade Lake @ \SI{2.80}{\giga\hertz}, internet downspeed ~\SI{1.8}{\giga\bit/\second}.
			\item[\alphtnotetext{2}] Effective speed while downloading multiple packages in parallel.
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

Additionally, some npm packages contain minified sources only that are still searchable valid code but can provide a significantly reduced readability.

@@

The spatial distance varies for the different views of the tool:
For the dependency browser and the usage browser, a separate toolbar has to be opened, which indicates a higher spatial distance; still, the artifacts are available in the same IDE.
Also, the dependency artifacts have no strong relationship to any existing IDE artifacts, so any closer integration into an existing view would increase coupling between independent domains.
The code annotations are displayed close to the original source code with a small spatial distance.

>>>>

Besides the precision of collected dependencies, their recall is also of interest.
As the dependencies are collected in excerpts from two very large datasets, a quantitative analysis of false-negative hits based on manual annotation of these datasets would be too expensive for this paper.
Nevertheless, some causes will prevent a dependency from being found by our methods:

@@

	\centering
	\begin{threeparttable}
		% Fix font size of \thead
		\renewcommand\theadfont{\normalsize}
		\input{sections/5_evaluation/resqu1/performance}
		\begin{tablenotes}
			\footnotesize
			\item[\alphtnotetext{1}] Hardware specifications of the test machine: 7 vCPUs Intel Xeon Cascade Lake @ \SI{2.80}{\giga\hertz}, internet down speed ~\SI{1.8}{\giga\bit/\second}.
			\item[\alphtnotetext{2}] Effective speed while downloading multiple packages in parallel.
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

Additionally, some npm packages contain minified sources only that are still searchable valid code but can provide significantly reduced readability.

@@

The spatial distance varies for the different views of the tool:
For the dependency browser and the usage browser, a separate toolbar has to be opened, which indicates a higher spatial distance; still, the artifacts are available in the same IDE.
Also, the dependency artifacts have no strong relationship to any existing IDE artifacts, so any closer integration into an existing view would increase coupling between independent domains.
The code annotations are displayed close to the package source code with a small spatial distance.

### 2021-10-12 docs/paper/sections/6_conclusion.tex

Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent, and that the resource requirements of our implementation are sufficiently low for collecting all data on the local machine of a package developer.
Nevertheless, we have identified a number of causes for false negatives over the whole mining process that are predestined to biasing the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.
Our analysis, however, is not yet fully supported by data and would require further quantitative evaluation to assess the exact precision and recall of our approach for mining usage samples as well as the efficacy of our tool.
As for the first question, manual annotation of source code repositories with usage samples will be required to compare them to the outputs of our implementation.
Close insights for the second question could be gained from a user study that compares the efficiency of package developers asked to solve a set of downstream dependency-related tasks with or without the help of our tool.

>>>>

Our analysis suggests that the collected dependencies and the extracted usage samples have a viable quality in terms of precision and extent and that the resource requirements of our implementation are sufficiently low for collecting all data on the local machine of a package developer.
Nevertheless, we have identified a number of causes for false negatives over the whole mining process that are predestined to biasing the output usage samples, including the popularity and recency of dependencies but also the proper declaration of packages and their renunciation of complex toolchains and metaprogramming patterns.
Our analysis, however, is not yet fully supported by data and would require further quantitative evaluation to assess the exact precision and recall of our approach for mining usage samples as well as the efficacy of our tool.
As for the first question, manual annotation of source code repositories with usage samples will be required to compare them to the outputs of our implementation.
Close insights for the second question could be gained from a user study that compares the efficiency of package developers asked to solve a set of downstream dependency-related tasks with or without the help of our tool.
